combo1

### 2024-04-01 Sections/Discussion.qmd
minor

## Overall Summary of Experiments 1-3

@@

## Modelling Interpretation
- why does Constant do better 
    - kind of task that permits for prior knowledge about 0
    - learning - end of training
- what does it suggest that the constant group was disproportionately well explained by the EXAM model?
-

### Limitations
- amount of training
- no mechanism to account for sequence effects in models
- more rigorous model comparison to account for exams greater complexity
- knowledge of function

>>>>

*Experimental Result Summary*

@@

*Modeling Summary*
EXAM is the best model for both groups, but EXAM does relatively good at accounting for the constant group. May have seemed counterintuitive, if one assumed that multiple, varied, examples were necessary to extract a rule. But, EXAM is not a conventional rule model - it doesn't require explictly abstract of a rule, but rather the rule-based response occurs during retrieval. The constant groups formation of a single, accurate, input-output association, in combination with the usefulness of the zero point, may have been sufficient for EXAM, and the constant group,  to perform well.

One concern may have been that the assumption of participants making use of the zero point turned the extrapolation problem into an interpolation problem - however this concern is ameliorated by the consistency of the results across both the original and reverse order conditions.

- why does Constant do better 
    - kind of task that permits for prior knowledge about 0
    - learning - end of training
- what does it suggest that the constant group was disproportionately well explained by the EXAM model?
-

*Limitations*
- amount of training
- constant group always having more experience at nearest position
- constant group having more extrapolation items
- only training and extrapolation - no interpolation items - so harder to make claims about extrapolation specifically, as opposed to generalization in general. 
- no mechanism to account for sequence effects in models
- more rigorous model comparison to account for exams greater complexity
- knowledge of function
